Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions

### 2024-09-27 outputs/paper/paper.qmd
made changes to the abstract

---
title: "Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions"
author: 
  - Yingke He
thanks: "Code and data are available at: https://github.com/ohyykk/ferrySale.git"
date: 09-23-2024
date-format: long
abstract: "This study examines the ticket redemption and sales counts for the Toronto Island Ferry, analyzing time-based trends and the relationships between sales and redemptions. Statistical models are developed to predict ferry ticket usage. The results provide insights into usage patterns, highlight operational considerations, and suggest avenues for future research. The analysis reveals distinct seasonal peaks and troughs in ferry usage, correlating with tourism and weather conditions. Furthermore, the study identifies discrepancies between ticket sales and redemptions, suggesting potential improvements in ticketing strategies and resource allocation."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
toc: true
bibliography: references.bib
---

@@

The remainder of this paper is structured as follows: Section 2 introduces the dataset used for the analysis, explaining the key variables and presenting key data analysis. Section 3 discusses the implications of the findings and potential directions for future research. Additional information is presented in the appendix at section A. @citeR and @rohan is utilized for the coding proposes of this paper, and the data section is referenced using @sec-data.

@@

The table @tbl-cleaned_data provides a detailed snapshot of the Toronto Island Ferry ticket transactions for a specific time period. It includes a unique ID for each transaction, the Time at which each transaction occurred, the number of Tickets Redeemed, the number of Tickets Sold, and the Date of the transaction.
```{r}
#| label: tbl-cleaned_data
#| echo: false

@@

# Create the table using kable
kable(table_data, col.names = c('ID', 'Time', 'Tickets Redeemed', 'Tickets Sold', 'Date'), 
      align = "c", 
      caption = "Table 1: Sample of cleaned Ferry Ticket Counts Data")

@@

This table shows the typical flucuations in ticket sales and redemptions throughout the day. For example, during late evening hours, we observe varying ticket redemption and sales patterns, which may correspond to changes in passenger demand as the ferry service approaches the end of its operational hours.

@@

# Create the table using kable
knitr::kable(summary_stats, col.names = c('Avg Redeemed', 'Avg Sold', 'Max Redeemed', 'Max Sold', 'Count'), 
      align = "c", caption = "Table 2: Summary Statistics of Ticket Counts")

```
The summary statistics, shown in Table 2, provide a clear understanding of ferry ticket trends. The high volume of tickets sold and redeemed indicates strong demand for the ferry service, with the close alignment between sales and redemptions suggesting high customer engagement. On average, 46.36 tickets were sold every 15 minutes during working hours, and 48.45 tickets were redeemed, highlighting that most customers have used their tickets. The small gap between sales and redemptions implies a few no-shows or unused tickets. The maximum values of 7,216 for sales and 7,229 for redemptions demonstrate the ferry’s capacity to handle high passenger volumes, typically operating at full capacity on busy days.

@@

The scatter plot analysis in Section 2.3 (Figure @fig-scatterPlot) demonstrated a generally positive correlation between ticket sales and redemptions, suggesting that most tickets purchased are used. However, discrepancies where sales exceed redemptions could be linked to bulk purchases, advanced ticket sales, or unredeemed tickets due to factors like adverse weather conditions. This observation is consistent with the analysis by @kopystynski1979potential, who highlighted the complexities of integrating ferry systems into urban transit networks. Understanding these discrepancies is critical for improving ticketing policies and service offerings to better match supply with demand.

>>>>

---
title: "Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions"
author: 
  - Yingke He
thanks: "Code and data are available at: https://github.com/ohyykk/ferrySale.git"
date: 09-23-2024
date-format: long
abstract: "This study examines the ticket redemption and sales counts for the Toronto Island Ferry, analyzing time-based trends and the relationships between sales and redemptions. Statistical models are developed to predict ferry ticket usage. The results uncover seasonal trends, operational inefficiencies, and discrepancies between ticket sales and redemptions, highlighting the need for improved resource management and service adjustments to better align with fluctuating passenger demand. These findings offer insights into usage patterns, operational considerations, and suggest avenues for future research, particularly in optimizing ticketing strategies and resource allocation."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
toc: true
bibliography: references.bib
---

@@

The remainder of this paper is structured as follows: @sec-data introduces the dataset used for the analysis, explaining the key variables and presenting key data analysis. @sec-discussion discusses the implications of the findings and potential directions for future research. Additional information is presented in the appendix at @sec-appendix. @citeR and @rohan is utilized for the coding proposes of this paper, and the data section is referenced using @sec-data.

@@

@tbl-cleaned_data provides a detailed snapshot of the Toronto Island Ferry ticket transactions for a specific time period. It includes a unique ID for each transaction, the Time at which each transaction occurred, the number of Tickets Redeemed, the number of Tickets Sold, and the Date of the transaction.
```{r}
#| label: tbl-cleaned_data
#| echo: false

@@

# Create the table using kable
kable(table_data, col.names = c('ID', 'Time', 'Tickets Redeemed', 'Tickets Sold', 'Date'), 
      align = "c", 
      caption = "Sample of cleaned Ferry Ticket Counts Data")

@@

The above table shows the typical flucuations in ticket sales and redemptions throughout the day. For example, during late evening hours, we observe varying ticket redemption and sales patterns, which may correspond to changes in passenger demand as the ferry service approaches the end of its operational hours.

@@

# Create the table using kable
knitr::kable(summary_stats, col.names = c('Avg Redeemed', 'Avg Sold', 'Max Redeemed', 'Max Sold', 'Count'), 
      align = "c", caption = "Summary Statistics of Ticket Counts")

```
The summary statistics, shown in @tbl-summary_stats, provide a clear understanding of ferry ticket trends. The high volume of tickets sold and redeemed indicates strong demand for the ferry service, with the close alignment between sales and redemptions suggesting high customer engagement. On average, 46.36 tickets were sold every 15 minutes during working hours, and 48.45 tickets were redeemed, highlighting that most customers have used their tickets. The small gap between sales and redemptions implies a few no-shows or unused tickets. The maximum values of 7,216 for sales and 7,229 for redemptions demonstrate the ferry’s capacity to handle high passenger volumes, typically operating at full capacity on busy days.

@@

The scatter plot analysis in Section 2.3 (@fig-scatterPlot) demonstrated a generally positive correlation between ticket sales and redemptions, suggesting that most tickets purchased are used. However, discrepancies where sales exceed redemptions could be linked to bulk purchases, advanced ticket sales, or unredeemed tickets due to factors like adverse weather conditions. This observation is consistent with the analysis by @kopystynski1979potential, who highlighted the complexities of integrating ferry systems into urban transit networks. Understanding these discrepancies is critical for improving ticketing policies and service offerings to better match supply with demand.
